
## Finalfit

help you quickly create elegant final results tables and plots when modelling in R. 

These can easily be exported as Word documents, PDFs, or html files.



### Install

```{r}

install.packages("finalfit")

install.packages("dplyr")

```

It is recommended that this package is used together with dplyr which can be installed via:



Documentation

The package documentation is maintained independently at finalfit.org.

Examples

See getting started and the All tables vignettes for extensive examples.

Crosstable / table 1

### Crosstable 

```{r}
library(dplyr)
library(finalfit)
explanatory = c("age.factor", "sex.factor", "obstruct.factor")

dependent = 'mort_5yr'

colon_s %>%

  summary_factorlist(dependent, explanatory, 

  p=TRUE, add_dependent_label=TRUE) -> t2

knitr::kable(t2, row.names=FALSE, align=c("l", "l", "r", "r", "r"))

```
### Regression table
```{r}
explanatory = c("age.factor", "sex.factor", 
  "obstruct.factor", "perfor.factor")
dependent = 'mort_5yr'
colon_s %>%
  finalfit(dependent, explanatory, metrics=TRUE) -> t7
knitr::kable(t7[[1]], row.names=FALSE, align=c("l", "l", "r", "r", "r", "r"))
knitr::kable(t7[[2]], row.names=FALSE, col.names="")
```

### Regression plots
```{r}
explanatory = c("age.factor", "sex.factor", 
  "obstruct.factor", "perfor.factor")
dependent = 'mort_5yr'
colon_s %>%
  or_plot(dependent, explanatory)
 ```
